\chapter{Conclusion}\label{Sect:conclusion}
\par The models produced were satisfactorily successful. Each provided great insight into which parameters build useful models. Though some models are useful, none are without errors. Using the ``best" model, as mentioned in Chapter \ref{Sect:results}, new data on silver-platinum crystal configurations can be produced.


\section{Future Work}\label{Sect:futureWork}
\par Using a small set of accurate DFT data, the code written to produce the model in Chapter \ref{Sect:procedureConstruction} can be easily adapted to construct models for compounds other than Ag-Pt. Such research could be used to determine which compounds can be accurately predicted using a simple pair-interaction model. A successful model can quickly predict formation energies for a variety of crystal configurations. These formation energies could then be used to construct the material’s phase diagram and determine which phases are thermodynamically stable.
\par Because the models produced in this paper used only pair-interactions, their effectiveness is limited by their simplicity. Implementation of three-body interactions has the potential to greatly increase the accuracy of these models.
%\par Citations yet to be included: \cite{_AFLOW} \cite{Kohn1965} \cite{curt2005scienceandtech} \cite{curtarolo2003predicting} \cite{Kresse:1999wc} \cite{kresse1993abinitio} \cite{Blochl:1994dx} \cite{kresse1996efficiency} \cite{monkhorst1976special} \cite{sanchez1984generalized} \cite{laks1992efficient} \cite{lerch2009uncle} \cite{cockayne2010building} \cite{nelson2013compressive}